### 2022-01-26 input/introduction.tex
add two comments in the introduction

To mitigate the broadcasting overhead, a \process creating a replica
should notify all and only \processes that have no closer replica in
the system. This would create interconnected sets of \processes, or
\emph{partitions}, gathered around a \emph{source} being their
respective replica. A \process deleting its replica should notify all
members of its partition so they can identify and rally their new
closest partition. \TODO{Periodic advertisement protocols} already
provide both
operations~\cite{hemmati2015namebased,sohier2012physarum}. However,
their functioning requires
% TODO: A periodic protocol... why a periodic protocol solves the ''correct cast/scope''? I miss the point here 
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item the use of synchronous communications~\cite{sohier2012physarum}
  or physical-time-based intervals tuned according to network topology
  parameters such as network diameter~\cite{hemmati2015namebased}.
\end{inparaenum}

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes can join, leave, or crash at any time. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.
  \textcolor{red}{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}

@@

As such, \NAME can constitute a novel building block for
geo-distributed services, \eg by efficiently sharing the locations of
replicated web objects in the vicinity of downloading nodes, or by
enabling efficient resource discovery in the vicinity of a region.
\TODO{More detail, name drop that we can support CDN.}

%% Then, we propose \emph{\NAME}, a logical partitioning protocol that
%% uses \underline{s}coped broad\underline{cast} to \underline{a}dapt its
%% partitions, \ie scopes, to creations and deletions of partitions in
%% the system. Each source advertises its existence to all possibly
%% interested \processes, \ie only interconnected \processes of its
%% partition plus \processes bordering its partition. In turns, \NAME
%% scales well to the number of sources since the higher the number of
%% partitions, the earlier the dissemination stops.

>>>>

To mitigate the broadcasting overhead, a \process creating a replica
should notify all and only \processes that have no closer replica in
the system. This would create interconnected sets of \processes, or
\emph{partitions}, gathered around a \emph{source} being their
respective replica. A \process deleting its replica should notify all
members of its partition so they can identify and rally their new
closest partition. Periodic advertisement protocols \note{Why a periodic protocol solves the ''correct cast/scope''? I miss the point here}
already provide both operations~\cite{hemmati2015namebased,sohier2012physarum}. However,
their functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item the use of synchronous communications~\cite{sohier2012physarum}
  or physical-time-based intervals tuned according to network topology
  parameters such as network diameter~\cite{hemmati2015namebased}.
\end{inparaenum}

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes can join, leave, or crash at any time. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast}
 \note{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}
  that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.

@@

As such, \NAME can constitute a novel building block for
geo-distributed services, \eg by efficiently sharing the locations of
replicated web objects in the vicinity of downloading nodes, or by
enabling efficient resource discovery in the vicinity of a region.
\note{More detail, name drop that we can support CDN.}
\note{Why C/P abstract sentence here? I would rather skip here and C/P and complete in the conclusion?}
%% Then, we propose \emph{\NAME}, a logical partitioning protocol that
%% uses \underline{s}coped broad\underline{cast} to \underline{a}dapt its
%% partitions, \ie scopes, to creations and deletions of partitions in
%% the system. Each source advertises its existence to all possibly
%% interested \processes, \ie only interconnected \processes of its
%% partition plus \processes bordering its partition. In turns, \NAME
%% scales well to the number of sources since the higher the number of
%% partitions, the earlier the dissemination stops.
